\documentclass[a4paper,10pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{parskip}
\usepackage[margin=0.55in]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[unicode, draft=false]{hyperref}
\usepackage{fontawesome5}

\titleformat{\section}{\normalsize\scshape\raggedright\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{5pt}{3pt}
\hypersetup{colorlinks,breaklinks,urlcolor=blue,linkcolor=blue}
\pagestyle{empty}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=1.1em,itemsep=-0.25em,topsep=0.05em}

\begin{document}

\begin{center}
\textbf{\Large ÉTIENNE COMPÉRAT}\\[-1pt]
\textbf{Predoctoral Fellow in Economics, University of Zurich}\\[-1pt]
\href{https://ecomperat.github.io}{\raisebox{-0.05\height}\faGlobe\ Website} \ $|$ \
\href{https://github.com/ecomperat}{\raisebox{-0.05\height}\faGithub\ GitHub} \ $|$ \
\href{https://www.linkedin.com/in/\%C3\%A9tienne-comp\%C3\%A9rat-a22850242/}{\raisebox{-0.05\height}\faLinkedin\ LinkedIn} \ $|$ \
\href{mailto:etienne.comperat@sciencespo.fr}{\raisebox{-0.05\height}\faEnvelope\ E-Mail}\\[-1pt]
\textbf{Research Interests:} Economic History, Political Economy, Spatial and Regional Economics
\end{center}

\section{Education}

\textbf{Sciences Po} \hfill 2023--2025 \\
M.Res. in Economics, PhD Track. Thesis (16/20): ``Enrichissez-vous!'': Education, Suffrage, and Local Development in July Monarchy France. Awarded Sciences Po Prize for Best Master's Thesis.

\textbf{University of California, Berkeley} \hfill 2022--2023 \\
Full-Year Exchange Program, B.A., Dept. of Agricultural \& Resource Economics \hfill GPA: 4.0

\textbf{Sciences Po} \hfill 2020--2023 \\
B.A. in Economics and Political Science \hfill \textit{Cum laude}

\section{Research Experience}

\textbf{Predoctoral Fellow in Economics} $|$ University of Zurich \hfill July 2025--Present \\
Supervisor: Hans-Joachim Voth
\begin{itemize}
  \item Build reproducible historical data pipelines from archival, textual, administrative, and geospatial sources for a project set in Revolutionary France; conduct historical geocoding and GIS integration.
  \item Contribute to computer-vision workflows for historical images, including preprocessing, labelling, supervised model training, feature extraction, and name extraction.
  \item Contributed reproducible code to the replication package for \textit{Fighting for Growth}.
\end{itemize}

\textbf{JPE Replicator} $|$ University of Chicago \hfill July 2025--Present \\
Data Editor: Florian Oswald
\begin{itemize}
  \item Conduct independent replications of accepted \textit{Journal of Political Economy} articles: verify tables and figures, review code, diagnose data and code issues, rebuild software environments, and prepare reports.
\end{itemize}

\textbf{Research Assistant} $|$ Sciences Po \hfill Summer 2025 \\
Supervisor: Roberto Galbiati
\begin{itemize}
  \item Collected, transcribed, and cleaned archival donor records to construct an individual-level dataset on anti-Dreyfusard mobilisation in late nineteenth-century France.
\end{itemize}

\textbf{EJ Replicator} $|$ Royal Economic Society \hfill 2024--July 2025 \\
Conducted reproducibility checks for accepted \textit{The Economic Journal} articles under editorial supervision.

\textbf{Research Assistant} $|$ Sciences Po; UC Berkeley; CEPREMAP \hfill 2023--2024
\begin{itemize}
  \item Constructed and documented administrative and historical datasets from police reports, press sources, death notices, French customs reports, and well-being-economics sources.
\end{itemize}

\section{Methods \& Programming}

\textbf{Empirical methods:} causal inference, panel data, spatial analysis, text analysis, computer vision. \\
\textbf{Historical data:} archival data construction, historical GIS and geocoding, OCR, web scraping, record linkage. \\
\textbf{Programming:} Python, R, Stata (advanced), Julia (intermediate). \\
\textbf{Tools:} Git, \LaTeX, QGIS, Google Vertex AI, reproducible workflows.

\section{Graduate Coursework}

\textbf{Core:} Econometrics I--III; Macroeconomics I--III; Microeconomics I--II. \quad
\textbf{Fields:} Economic History; Political Economy; Urban \& Regional Economics; International Trade; Demography. \quad
\textbf{Computational:} Dynamic Programming; Incomplete-Market Models; Numerical Solution Methods.

\section{Languages}

\textbf{Native:} French \ $|$ \ \textbf{C2:} English \ $|$ \ \textbf{C1:} Italian \ $|$ \ \textbf{B1:} German

\vfill
\center{\footnotesize Last updated: May 2026}

\end{document}
